Pool Model

### 2025-08-28 pool_model.tex
reorder package imports

\documentclass[10pt,A4paper]{article}
\usepackage[
    a4paper,
    inner=2.5cm,
    outer=3cm
]{geometry}

\usepackage[utf8]{inputenc}
\usepackage[a4paper,
            inner=2.5cm,
            outer=3cm
            ]{geometry}
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off, font=small]{caption}            
\usepackage{acronym}
\usepackage{graphicx}% Include figure files
\usepackage{bm}% bold math
\usepackage{color}
\usepackage{hyperref}
\usepackage[backend=biber,
            sorting=none,
%            citestyle=numeric-comp,
%\            bibstyle=ieee, 
            style=numeric-comp,
            hyperref=true,
            maxnames=2,
            url=false,
            isbn=false,
            eprint=false,
            date=year,
            doi=false,
            giveninits=true
            ]{biblatex}
\addbibresource{references.bib}
\usepackage{xpatch}
\xpatchbibmacro{journal+issuetitle}{%
\usebibmacro{journal}%
\setunit*{\addspace}%
}{%
\usebibmacro{journal}%
\setunit*{\addcomma\space}%
}{}{}

\renewbibmacro*{name:andothers}{% Based on name:andothers from biblatex.def
  \ifboolexpr{
    test {\ifnumequal{\value{listcount}}{\value{liststop}}}
    and
    test \ifmorenames
  }
    {\ifnumgreater{\value{liststop}}{1}
       {\finalandcomma}
       {}%
     \andothersdelim\bibstring[\emph]{andothers}}
    {}}

%\DeclareFieldFormat[article]{title}{#1}
\DeclareFieldFormat[article]{volume}{\textbf{#1}}
%\DeclareFieldFormat[book]{volume}{\textbf{#1}}

\renewcommand\newunitpunct{\addcomma\space}
\DefineBibliographyStrings{english}{%
page = {},
pages = {},
}

\renewbibmacro{in:}{\addcomma\addspace}

\renewbibmacro*{volume+number+eid}{%
\isdot
\printfield{volume}%
\setunit*{\addcomma\addspace}%
\iffieldundef{number}{}{%
\printtext{no\adddot\addnbthinspace}%
}%
\printfield{number}%
\setunit{\addcomma\space}%
\printfield{eid}}

\setlength{\tabcolsep}{1.3pt}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{mathrsfs}
\usepackage[T1]{fontenc}
\usepackage{diagbox}
\usepackage{here}
\usepackage[dvipsnames]{xcolor}
\usepackage{lipsum}
\usepackage{multirow}
\usepackage{ctable} % for \specialrule command
\usepackage{array,booktabs}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
\usepackage{subcaption}
\usepackage{float}
\usepackage{tabularx}
\usepackage{siunitx}
\usepackage{listings}
\usepackage{listings-rust}
\lstset{
    language=Rust,
    showstringspaces=false
}
\usepackage{newfloat}
\DeclareFloatingEnvironment[
  name=Listing,
  listname=List of Listings,
  within=section,
]{listing}
\restylefloat{table}
\numberwithin{equation}{section}

>>>>

\documentclass[10pt,A4paper]{article}
\usepackage[utf8]{inputenc}

\setlength{\tabcolsep}{1.3pt}
\usepackage{acronym}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[
    backend=biber,
    sorting=none,
    style=numeric-comp,
    hyperref=true,
    maxnames=2,
    url=false,
    isbn=false,
    eprint=false,
    date=year,
    doi=false,
    giveninits=true
]{biblatex}
\usepackage{array}
\usepackage{bm}
\usepackage{booktabs}
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off, font=small]{caption}
\usepackage{color}
\usepackage{ctable} % for \specialrule command
\usepackage{diagbox}
\usepackage{float}
\usepackage[T1]{fontenc}
\usepackage[a4paper,inner=2.5cm,outer=3cm]{geometry}
\usepackage{graphicx}% Include figure files
\usepackage{here}
\usepackage{hyperref}
\usepackage{lipsum}
\usepackage{listings}
\usepackage{listings-rust}
\usepackage{mathtools}
\usepackage{mathrsfs}
\usepackage{multirow}
\usepackage{newfloat}
\usepackage{siunitx}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage[dvipsnames]{xcolor}
\usepackage{xpatch}

% Define new column type with multirow
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}

% Add bibliography
\addbibresource{references.bib}

% Define Rust lisintgs
\lstset{
    language=Rust,
    showstringspaces=false
}
\DeclareFloatingEnvironment[
  name=Listing,
  listname=List of Listings,
  within=section,
]{listing}

\restylefloat{table}

% Define equation numbering
\numberwithin{equation}{section}
